From physical principles to ???

### 2016-03-25 2015CompleteDerivation/completeDerivation.tex
Different argument for second countable

We claim $\mathcal{S}$ has a topology $\mathcal{T}$. Consider the set of all possible physical outcomes associated with all physical processes. Each possible outcome is associated with a set of states that are compatible with that outcome. Let $\mathcal{T}$ be the set of all sets associated with all physical outcomes. $\mathcal{S} \in \mathcal{T}$ and is associated with unavoidable outcomes. $\varnothing \in \mathcal{T}$ and is associated with impossible outcomes. Let $V_1, V_2 \in \mathcal{T}$. Then, by definition, there exist a process $P_1$ that admits $V_1$ as an outcome and a process $P_2$ that admits $V_2$ as an outcome. Consider the process $P$ that combines the outcomes of $P_1$ and $P_2$. This always exist physically as we can prepare the same state multiple times and let it interact with each process separately. $P$ will have a possible outcome $V$ corresponding to the case where $P_1$ gave outcome $V_1$ and $P_2$ gave outcome $V_2$. The states compatible with $V$ must be in both $V_1$ and $V_2$, that is $V = V_1 \cap V_2$. Therefore $\mathcal{T}$ is closed under intersection. Let $V_1, V_2 \in \mathcal{T}$. If they are physically distinguishable, then there exists a physical process $P$ that admits both as outcomes. Given $P$, we can always construct the process $P_0$ that combines $V_1, V_2$ into a single outcome $V$ by "forgetting" which of the two was given. The states compatible with $V$ must be in either $V_1$ or $V_2$, that is $V = V_1 \cup V_2$. Therefore $\mathcal{T}$ is closed under union. $\mathcal{T}$ is a topology by definition.

We claim that $\mathcal{S}$ is Hausdorff. Let $\mathcal{s_1}, \mathcal{s_2} \in \mathcal{S}$. As states are physically distinguishable, there must exist a physical process with two outcomes $V_1, V_2 \in \mathcal{T}$ for which $s_1 \in V_1, s_2 \in V_2, V_1 \cap V_2 = \varnothing$. $\mathcal{S}$ is Hausdorff by definition.

We claim that $\mathcal{S}$ is second countable. Consider the set of outcomes of a process. As each is identified by a finite number of digits. The set of outcomes is countable. This remains true when combining processes: the number of processes we can combine is finite as so it is the number of times we can prepare the same state and the intersections of countable many sets is still countable. Consider now the set, not necessarily finite, of all processes $\mathcal{P}$ that cover the whole space (i.e. union of outcomes is the whole space). Consider now the super process $P_s$ that is the combination of all elements in $\mathcal{P}$. This represents the best possible identification of each state, as no other process can further refine the set of possibilities. As states are physically distinguishable, their best possible identification must be reachable by a physical process. The outcomes of $P_s$ are countable. The set of outcomes represent a basis for the topology because given the outcome of this super process we can construct the outcome of all other less refined processes. The topology has a countable basis. $\mathcal{S}$ is second countable by definition.

>>>>

We claim $\mathcal{S}$ has a topology $\mathsf{T}$. Consider the set of all possible physical outcomes associated with all physical processes. Each possible outcome is associated with a set of states that are compatible with that outcome. Let $\mathsf{T}$ be the set of all sets associated with all physical outcomes. $\mathcal{S} \in \mathsf{T}$ and is associated with unavoidable outcomes. $\varnothing \in \mathsf{T}$ and is associated with impossible outcomes. Let $V_1, V_2 \in \mathsf{T}$. Then, by definition, there exist a process $P_1$ that admits $V_1$ as an outcome and a process $P_2$ that admits $V_2$ as an outcome. Consider the process $P$ that combines the outcomes of $P_1$ and $P_2$. This always exist physically as we can prepare the same state multiple times and let it interact with each process separately. $P$ will have a possible outcome $V$ corresponding to the case where $P_1$ gave outcome $V_1$ and $P_2$ gave outcome $V_2$. The states compatible with $V$ must be in both $V_1$ and $V_2$, that is $V = V_1 \cap V_2$. Therefore $\mathsf{T}$ is closed under intersection. Let $V_1, V_2 \in \mathsf{T}$. If they are physically distinguishable, then there exists a physical process $P$ that admits both as outcomes. Given $P$, we can always construct the process $P_0$ that combines $V_1, V_2$ into a single outcome $V$ by "forgetting" which of the two was given. The states compatible with $V$ must be in either $V_1$ or $V_2$, that is $V = V_1 \cup V_2$. Therefore $\mathsf{T}$ is closed under union. $\mathsf{T}$ is a topology by definition.

We claim that $\mathcal{S}$ is Hausdorff. Let $\mathcal{s_1}, \mathcal{s_2} \in \mathcal{S}$. As states are physically distinguishable, there must exist a physical process with two outcomes $V_1, V_2 \in \mathsf{T}$ for which $s_1 \in V_1, s_2 \in V_2, V_1 \cap V_2 = \varnothing$. $\mathcal{S}$ is Hausdorff by definition.

We claim that $\mathcal{S}$ is second countable. Consider the set of outcomes of a process. As each is identified by a finite number of digits. The set of outcomes is countable. This remains true when combining processes: the number of processes we can combine is finite as so it is the number of times we can prepare the same state and the intersections of countable many sets is still countable. Consider a bases for the topology. Suppose it is of cardinality greater than countability. Then no physical process could ever distinguish between the elements of the basis. The basis, and therefore the outcomes, would not be physically distinguishable. The basis for the topology cannot be of cardinality greater than countability. By contradiction, $\mathcal{S}$ must be second countable.
